Borel regularity for ODEs and Thimble Integrals

### 2023-11-07 exp-resurgence.tex
add pictures intersection thimbles

\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[ Howls]}.}

@@

@@

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$. We choose $n=4$ and $n=5$. }
    \label{fig:intersection_thimbles}
\end{figure}

@@

Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
\begin{align*}
    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
\end{align*}
\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
\subsubsection{An eye on resurgence}

@@

\section{Generalities about ODEs and Integral Equations}
\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}

>>>>

\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.}

@@

\begin{remark}
    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the Borel transform of $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}. Furthermore, expanding $\hat{\phi}_j$ at its critical points we recover the germs $\series{\phi}_k$ for $k\neq j$. This is an instance of resurgence, indeed according to the theory of Ecalle, $\hat{\phi}_j$ are all resurgent functions. We'll see an example in Section~\ref{sec:eye-res-airy}. 
\end{remark}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{figures/contour1-AL4--12.jpg}
    \includegraphics[scale=0.45]{figures/contour2-AL4--12.jpg}
    \includegraphics[scale=0.45]{figures/contour--AL4--12--inter.jpg}
    \includegraphics[scale=0.45]{figures/contour1-AL5--12.jpg}
    \includegraphics[scale=0.45]{figures/contour2-AL5--12.jpg}
    \includegraphics[scale=0.45]{figures/contour--AL5--12--inter.jpg}
    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$. We choose $n=4$ and $n=5$. }
    \label{fig:intersection_thimbles}
\end{figure}

@@

Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
\begin{align*}
    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
\end{align*}
\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
\subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behaviour near the singular points. A prototypical class of resurgent functions is the so-called simple resurgent functions, namely analytic function $\hat{\phi}$ with singularities $\omega$ such that 
\begin{align*}
    \hat{\phi}(\zeta-\omega)=\frac{S_\omega}{2\pi i} \log(\zeta) \series{\phi}_\omega(\zeta) + \text{ hol. funct.}
\end{align*}
where $S_\omega$ is a constant, typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$. The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.  
The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$  
Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent functions. Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$. Hence the set of singularities is given by the critical values of $f$.  Since $f$ has finitely many critical values, we can

@@

\subsection{Picard--Lefschetz formula in pictures}
We'll compute the Picard--Lefschetz formula as intersection of the base of thimbles and its dual, relative the singular direction $\theta=0$. We'll do it graphically, by plotting the steepest decent contours center at the critical points of $f$. We'll consider the example of Airy and Airy--Lucas with $n=4$.

For the classical Airy function, we have a two dimensional base of thimbles, thus we have to compute only one intersection:
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/contour1--airy.jpg}
    \includegraphics[scale=0.7]{figures/contour2--airy.jpg}
     \includegraphics[scale=0.7]{figures/contour--Airy--intersection.jpg}
    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$. With respect to the Stokes line $\theta=0$, we choose $\theta=0.1$ for the picture on the left and $\theta=-0.1+\pi$ for the picture in the center. The picture on the right shows the intersection of the thimbles which is given by a single point. Thus up to normalization, the Stokes constant is $1$. The images were obtained with Mathematica, and the thimbles are computed as the steepest descent contours from the critical points.}
    \label{fig:intersection_thimbles-Airy}
\end{figure}
We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{sec:eye-res-airy}.

For Airy--Lucas with parameter $n=4$, we have a three dimensional base of thimbles, graphically represented as 
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.35]{figures/thimble-n4.png}
    \caption{Caption}
    \label{fig:thimble-n4}
\end{figure}
Then computing intersections of dual pairs of thimbles we get 
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.4]{figures/contour1-AL4--12.jpg}
    \includegraphics[scale=0.4]{figures/contour2-AL4--12.jpg}
     \includegraphics[scale=0.4]{figures/contour--AL4--12--inter.jpg}
     \includegraphics[scale=0.4]{figures/contour1-AL4--13.jpg}
    \includegraphics[scale=0.4]{figures/contour2-AL4--13.jpg}
     \includegraphics[scale=0.4]{figures/contour--AL4--13--inter.jpg}
     \includegraphics[scale=0.4]{figures/contour1-AL4--32.jpg}
    \includegraphics[scale=0.4]{figures/contour2-AL4--32.jpg}
     \includegraphics[scale=0.4]{figures/contour--AL4--32--inter.jpg}
    \caption{First line computes the intersection of $\Lambda_1$ and $\Lambda_2$. Second line computed the interaction of $\Lambda_3$ and $\Lambda_2$. Third line computed the intersection of $\Lambda_3$ and $\Lambda_1$.}
    \label{fig:intersection_thimbles-AL4}
\end{figure}
Notice that $\Lambda_1$ and $\Lambda_3$ do not intersect as they are in the same class, because they are preimages of the same rays through infinity.   
\section{Generalities about ODEs and Integral Equations}
\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
